\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-02 paper/main.tex
finished drafts of all main and supplemental figures

\newcommand{\dynamicsRandom}{S1}
\newcommand{\dynamicsAdaptive}{S2}
\newcommand{\fingerprintsRandom}{S3}
\newcommand{\fingerprintsAdaptive}{S4}
\newcommand{\recallInit}{S5}

@@

@@

@@

% figure: fingerprint trajectories

% figure: carryover effects: clustering early vs. clustering late

% figure: clustering carryover vs. accuracy difference

% figure: clustering carryover vs. temporal clustering differences

>>>>

\newcommand{\dynamicsRandom}{S1}
\newcommand{\dynamicsAdaptive}{S2}
\newcommand{\accuracyByList}{S3}
\newcommand{\clusterCorrs}{S4}
\newcommand{\fingerprintsRandom}{S5}
\newcommand{\fingerprintsAdaptive}{S6}
\newcommand{\recallInit}{S7}
\newcommand{\fingerprintTrajectoryRandom}{S8}

@@

% figure: accuracy by list
Figure~\accuracyByList.

@@

% figure: correlations between clustering scores
Figure~\clusterCorrs.

@@

% figure: fingerprint trajectories
\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/fingerprint_trajectories}

    \caption{\textbf{Memory fingerprint dynamics (order manipulation
    conditions).} \textbf{A.} Each column (and color) reflects an experimental
    condition. In the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for one list. Order
    manipulation (early) lists are denoted by circles and randomly ordered
    (late) lists are denoted by stars. All of the fingerprints (across all
    conditions and lists) are projected into a common space. The bar plots in
    the bottom panels display the Euclidean distances of the per-list memory
    fingerprints to the list 0 fingerprint, for each condition. Error bars
    denote bootstrap-estimated 95\% confidence intervals. The dotted vertical
    lines denote the boundaries between early and late lists. \textbf{B.} In
    this panel, the fingerprints for early (circle) and late (star) lists are
    averaged across lists and participants before projecting the fingerprints
    into a (new) 2D space. See Figure~\fingerprintTrajectoryRandom~for
    analogous plots for the random (control) conditions. }
    \label{fig:fingerprint-trajectories}

% figure: carryover effects: 
%  - clustering early vs. clustering late
%  - clustering carryover vs. accuracy difference
%  - clustering carryover vs. temporal clustering differences
\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/clustering_carryover}

    \caption{\textbf{Feature clustering carryover effects.} \textbf{A.} Feature clustering scores for ordder manipulation (early) versus randomly ordered (late) lists.
    \textbf{B.}  Accuracy differences (on early versus late lists) versus feature clustering ``carryover'' (defined as the differences between the average clustering scores on early and late lists).
    \textbf{C.}  Temporal clustering differences (on early versus late lists) versus feature clustering carryover.  \textbf{All panels.} Each dot in the main scatterplots denotes the
    average scores for one participant. The colored regression lines are computed
    across participants. The inset displays condition-averaged results, where each
    dot reflects a single condition and the regression line is computed across
    experimental conditions. All error ribbons denote bootstrap-estimated 95\%
    confidence intervals.} \label{fig:clustering-carryover}
    \end{figure}

### 2023-01-02 paper/supplement.tex
finished drafts of all main and supplemental figures

@@

    \caption{\textbf{Memory ``fingerprints.'' (adaptive conditions).}
    The across-participant distributions of clustering scores for each feature
    type ($x$-coordinate) are displayed for each experimental condition
    (color), separately for order manipulation (early, top) and randomly
    ordered (late, bottom) lists.}
        \label{fig:fingerprints-adaptive}
\end{figure}

@@

\newpage
\renewcommand{\refname}{Supplementary references}
\bibliographystyle{apa}
\bibliography{CDL-bibliography/cdl}

>>>>

\begin{figure}[tp] \centering
    \includegraphics[width=0.75\textwidth]{figures/accuracy_by_list}

    \caption{\textbf{Recall accuracy by study list number.}  Each panel displays the average recall accuracy (across participants) as a function of the number of studied lists for the
    random (control) conditions (\textbf{A.}), order manipulation conditions (\textbf{B.}), and adaptive conditions (\textbf{C.}.  The conditions are denoted by color.  Note that the first four
    lists in all of the ``adaptive'' conditions were ordered randomly to compute a baseline fingerprint for each participant prior to initiating the adaptive ordering procedure.  All error
    ribbons denote bootstrap-estimated 95\% confidence intervals, calculated across participants.}
        \label{fig:accuracy-by-list}
\end{figure}

\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/clustering_correlations}

    \caption{\textbf{Correlations between feature clustering scores (order manipulation conditions).}  Each column reflects one experimental condition.  The matrices in the top and middle
    rows display across-participant correlations between clustering scores for each feature dimension (top: order manipulation lists; middle: randomly ordered lists).  The matrices
    in the bottom rows display the differences between the top and middle rows.}
        \label{fig:clustering-correlations}
\end{figure}

@@

@@

\begin{figure}[tp] \centering
    \includegraphics[width=\textwidth]{figures/fingerprint_trajectories_random}

    \caption{\textbf{Memory fingerprint dynamics (random conditions).}
    \textbf{A.} Each column (and color) reflects an experimental condition. In
    the top panels, each marker displays a 2D projection of the
    (across-participant) average memory fingerprint for one list. Early lists
    are denoted by circles and late lists are denoted by stars. All of the
    fingerprints (across all conditions and lists) are projected into a common
    space. The bar plots in the bottom panels display the Euclidean distances
    of the per-list memory fingerprints to the list 0 fingerprint, for each
    condition. Error bars denote bootstrap-estimated 95\% confidence intervals.
    The dotted vertical lines denote the boundaries between early and late
    lists. \textbf{B.} In this panel, the fingerprints for early (circle) and
    late (star) lists are averaged across lists and participants before
    projecting the fingerprints into a (new) 2D space.} \label{fig:fingerprint-trajectories-random}

    \end{figure}

% accuracy by list (list order effects)

% correlations between different types of clustering

%\newpage
%\renewcommand{\refname}{Supplementary references}
%\bibliographystyle{apa}
%\bibliography{CDL-bibliography/cdl}
